---
title: "test"
author: "Jian Li"
date: "11/4/2019"
output:
  html_document: default
  pdf_document: default
  word_document: default
  runtime: shiny
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Header 1
Some **bold**

My test link [NCEAS](http://www.nceas.ucsb.edu)
Another link [DataOne](http://www.dataone.org)

# Create a list

An ordered list:

1. NOLA
  * Terminal 1
  * Terminal 2
2. Santa Barbara
3. Hawaii Honolulu and then Toronto

# Busy airports

An ordered list:
1. Ohare
2. Santa Barbara - highly doubt it
3. Dallas



# Show an in-line R code
```{r}
x <- 3
y <- 3*x
summary(cars)
```
My results show a value of `r format(y,digits=3)`

# Find a sum of squares
```{r}
n <- 1:9
SS <- sum(n*n)
```

# Another chunk
The result is $\sum_{i=1}^N{i^2}=$ `r SS`

```{r, echo=FALSE}
numericInput("n", "How many cars?", 5)
renderTable({head(cars, input$n)})
```


# Function syntax
```{r, results='hide'}
result_value <- function(v1=0, v2=0) {}
weight_kg <- c(50, 45, 52)
mean(weight_kg)
```

# Read a csv file

Use `read.csv` to read in the data
```{r}
bg_chem <- read.csv("BGchem2008data.csv")
mean(bg_chem$CTD_Depth)
```

```{r}
plot(bg_chem$CTD_Depth, bg_chem$CTD_Temperature)
```


